NTM CT Scoring - Initial Agreement

### 2022-11-28 Stacey Martiniano/ntm_agreement.qmd
better agreement plots

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    toc: true
    toc-depth: 5
    toc-float: true
    self-contained: true
editor: visual
---

```{r}
#| include: false
library(dplyr)
library(irr)
library(redcapAPI)
# Import data
api <- read.table("~/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",header = F)
rcon <- redcapConnection(url = "https://redcap.ucdenver.edu/api/",
                         token = api[1,1])
data = exportRecords(rcon)
# Make scorer IDs by initial
data$scorer = paste0(toupper(substr(data$reader_first_name,1,1)),
                     toupper(substr(data$reader_last_name,1,1)))
data = data %>% arrange(scan_id,scorer) %>% filter(scan_id>2) %>% 
  select(scorer,scan_id,bronchiectasis_rul:atelectasis___6)
```

# Scan 3

## Bronchiectasis

```{r}
# Get relevant columns and prepare for Fleiss' kappa calculation
bronch = data %>% filter(scan_id==3) %>% 
  select(scorer,bronchiectasis_rul:bronchiectasis_lll)
rows = as.character(label(bronch)[-1])
cols = bronch$scorer
bronch = data.frame(t(bronch[,-1]))
rownames(bronch) = rows
colnames(bronch) = cols
```

>>>>

---
title: "NTM CT Scoring - Initial Agreement"
author: "Tim Vigers"
date: "`r format(Sys.time(), '%d %B %Y')`"
format:
  html:
    code-fold: true
    toc: true
    toc-depth: 5
    toc-float: true
    self-contained: true
    fig-height: 8
    fig-width: 10
editor: visual
---

```{r}
#| include: false
library(tidyverse)
library(irr)
library(redcapAPI)
library(Hmisc)
library(DT)
library(RColorBrewer)
# Import data
api <- read.table("~/Dropbox/Work/Vigers/CF/Stacey Martiniano/NTM CT Scoring/api.txt",
                  header = F)
rcon <- redcapConnection(url = "https://redcap.ucdenver.edu/api/",
                         token = api[1,1])
data = exportRecords(rcon,labels = F)
data = data.frame(lapply(data,as.character))
# Make scorer IDs by initial
data$scorer = paste0(toupper(substr(data$reader_first_name,1,1)),
                     toupper(substr(data$reader_last_name,1,1)))
# Select relevant columns, convert to long data
data = data %>% arrange(scan_id,scorer) %>% filter(scan_id>2) %>% 
  select(scorer,scan_id,bronchiectasis_rul:atelectasis___6)
data = data %>% pivot_longer(bronchiectasis_rul:atelectasis___6,
                             names_to = c("feature","location"),
                             names_pattern = "(.*)_(.*)$") %>%
  mutate(feature=gsub("__","",feature),
         feature = str_to_title(gsub("_"," ",feature)))
data$location = factor(data$location,
                       levels = c("1","2","3","4","5","6","ling","lll","lul","rll","rml","rul"),
                       labels = c("RUL","RML","RLL","LUL","Ling","LLL","Ling","LLL","LUL","RLL","RML","RUL"))
data$value = factor(data$value,levels = c("Checked","Unchecked","Absent","Cylindric","Varicose"))
vals = levels(data$value)
# One column per scorer
data = data %>% pivot_wider(names_from = scorer,values_from = value)
# Find disagreements
data$disagree = !(data$AF == data$DL & data$DL == data$JW)
# Set colors for whole document
n = length(vals)
name = "Accent"
colors <- brewer.pal(n,name)
names(colors) <- vals
custom_colors <- scale_fill_manual(name = "", values = colors)
```

# All disagreements

The table below is sortable and searchable, and includes only the features and locations where there was some disagreement.

```{r}
# Table
data %>% filter(disagree == T) %>% select(-disagree) %>% datatable(.,rownames = F)
```
# Plots

## All scans

```{r}
data %>% 
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_grid(rows = vars(scan_id),cols = vars(feature))
```

## Scan 3

```{r}
scan = 3
data %>% filter(scan_id == scan) %>%
  select(feature,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~feature)
```

## Scan 4

```{r}
scan = 4
data %>% filter(scan_id == scan) %>%
  select(feature,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~feature)
```

## Scan 5

```{r}
scan = 5
data %>% filter(scan_id == scan) %>%
  select(feature,location,AF:JW) %>%
  pivot_longer(AF:JW) %>%
  ggplot(.,aes(x=name,y=location,fill=value))+
  geom_tile(color = "black") + 
  theme_bw() + labs(fill="",x="Scorer",y="Location") +
  custom_colors+
  facet_wrap(~feature)
```

# Fleiss' Kappa by Feature

```{r}

```
